Visualizations for the manuscript

### 2022-03-28 metanalysis_visualization/manuscript_Figures.Rmd
heatmap added the vline and monthly X axis

tempVariabilityInput <- new('DataTemporalMap', probabilityMap = as.matrix(percentages_htm), 
         countsMap = as.matrix(counts_htm), dates = dates, support = as.data.frame(names(percentages_htm)), 
         variableName = "example", variableType = "character", period = "month")
plotDataTemporalMap(tempVariabilityInput, absolute = TRUE)

>>>>

tempVariabilityInput <- new('DataTemporalMap', probabilityMap = as.matrix(percentages_htm), 
         countsMap = as.matrix(counts_htm), dates = dates, support = as.data.frame(names(percentages_htm)), 
         variableName = "example", variableType = "character", period = "month")

vline <- function(x = 0, color = "green") {
  list(
    type = "line",
    y0 = 0,
    y1 = 1,
    yref = "paper",
    x0 = x,
    x1 = x,
    line = list(color = color, dash="dot"))
}

fig = plotDataTemporalMap(x)

fig <- fig %>%
  layout(
    title = " ",
    xaxis = list(
      type = 'date',
      tickformat = "%b-%y", 
      tickangle=-45, 
      tickvals=dates), 
    shapes = list(vline(as.Date("2020-03-15"))))

fig
